\documentclass[10pt, a4paper]{article}
    \usepackage{fullpage}
    \usepackage[margin=0.5in]{geometry}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[inline]{enumitem}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{hyperref}
    
    \pagestyle{empty}
    \raggedright
    \input{glyphtounicode}

\pdfgentounicode=1

\usepackage{fontawesome}


\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-15pt}\vspace*{3pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}


    \begin{document}




%==== Profile ====%
{\begin{center}
    
	{\Huge \scshape {Full Name}}\\
	\vspace{2mm}
	
\end{center}


%==== Education ====%

    \header{\textbf{Education}}

    \textbf{B.S. in Computer Science} \hfill GPA 4.00 | May 2025 (expected)
\\ State University \hfill Location

\textbf{Relevant Coursework}: Object-Oriented Programming and Data Structures, Digital Design, Calculus 1 and 2 \\


\vspace{2mm}



%%==== Experience ====%

    \header{\textbf{Work Experience}}
    \textbf{Software Engineer Intern } \\ 
    Large company     \hfill June 2022 - August 2022\\
    \vspace{-2mm}
\begin{itemize}
    \itemsep-0.05em
    \item Worked with the Web Team on -website name- to develop, test and release new features. Learned processes of development like collaborating with Git, using DevOps systems and building to different environemnts for QA testing.
    \item Collaborated with designers and followed Agile development processes to develop and deploy the product page for the -app name- app using HTML, SCSS and Javascript. 
    \item Researched and implemented iOS Smart Banners on all -page name- pages using PHP, and deployed the feature to over 50 million monthly users leading to a 10\% increase in -app name- App usage. 
    \item SSHed into servers to upload new image assets, perform ecommerce republishing and run data migration scripts. 
\end{itemize}

    \textbf{Teaching Assistant } \\ -Class Name- \hfill January 2022 - Present\\
      
    \begin{itemize}
        \vspace{-2mm}
        \itemsep-0.05em
        \item Assisted over 50 students every week to make progress on their project, prepare for pitch competitions, and meet deadlines with results. 
        \item Guided students on programming concepts for their projects, good implementation of code, and preparing design documents.
        \item Hosted two hour long skill sessions for 100+ students on how to develop technical skills like Java and how to use Tableau.
    \end{itemize}


\header{\textbf{Projects}}
\textbf{-Name of Project-} \\ \textit{-Name of hackathon}
\hfill July 2022\\
\vspace{-2mm}
\begin{itemize}
    \itemsep-0.05em
    \item Created a three-dimensional visualization of the history of -popular media- using Three.js for -company name-'s internal hackathon event and presented it to the Digital Media department. 
    \item Collaboated virtually with a team to collect, clean and analyze data from the last 13 years of -popular media-.
\end{itemize}
\textbf{Diabetes Predictor} \\ \textit{Personal Project}
\hfill February 2022\\
\vspace{-2mm}
\begin{itemize}
    \itemsep-0.05em
    \item Applied the RandomForestClassifier algorithm, and used Python and pandas to train a Machine learning model to predict the possibility of onset of diabetes based on factors like Age, Insulin levels, and genetics.
    \item Used Streamlit to build, display statistics and visualizations and host this model online. 
\end{itemize}
\textbf{-Project Name} \\  \textit{-Name of class-} 
\hfill August 2021 - May 2022\\
\vspace{-2mm}
\begin{itemize}
    \itemsep-0.05em
    \item Designed webapp in Figma and coordinated with team to build a functional prototype webapp with React, Typescript, and Node.js in less than 2 weeks, in time for a pitch competition. 
    \item Integrated MySQL with the webapp for users to be able to sign in and interact with external hardware.
    
\end{itemize}

\textbf{Maze Traversing Autonomous Car} \\ \textit{-Name of class-}
\hfill September 2021 - December 2021\\
\vspace{-2mm}
\begin{itemize}
    \itemsep-0.05em
    \item Designed and deployed a self-driving car that can navigate through any given configuration of a maze in under 2 minutes, and respond to color cues to start, pause and stop the car, as well as pick up and drop off passengers. 
    \item Devised the algorithm, and leveraged MATLab to program the car, and set up external sensors while working with a team to meet strict weekly deadlines. 
\end{itemize}



\header{\textbf{Technical Skills}}

\textbf{Languages and Frameworks}: Java, Python, HTML5, CSS3, Javascript, Typescript, React, Redux, MySQL \\
\textbf{Tools}: AWS, Figma, Git, Github, Windows, MacOS, Excel, Airtable, \LaTeX, Tableau \\
\vspace{3mm}

\header{\textbf{Extracurriculars}}


\textbf{Student Clubs:} -Names of clubs- \\
\textbf{Hackathons:} -Names of hackathons-




    



\end{document}
