\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage[margin=0.6in]{geometry}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[inline]{enumitem}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{hyperref}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

\usepackage{fontawesome}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-15pt}\vspace*{3pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}



\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-30.9pt}



%==== Profile ====%
\vspace{-1mm}
\begin{center}
	{\Huge \scshape {Omkaar Shenoy}}\\
	\vspace{2mm}
	\faPhone  \hspace{0.5mm} (341)-345-7209 $\cdot$ \href{mailto:omkaarshenoyos@gmail.com}{\faEnvelope \hspace{0.5mm} omkaarshenoyos@gmail.com} \hspace{0.5mm}   $\cdot$ \href{https://www.linkedin.com/in/OmkaarShenoy/}{\faLinkedin/OmkaarShenoy} $\cdot$ \href{https://github.com/OmkaarShenoy}{\faGithub/OmkaarShenoy}
	
\end{center}


%==== Education ====%


    \header{\textbf{Education}}

    \textbf{BS Computer Science} \hfill GPA 4.25 | May 2025 (expected)
\\ Arizona State University \hfill Tempe, Arizona
 
New American University Scholar, Fulton Ambassador, \href{https://gcsp.engineering.asu.edu/}{Grand Challenge Scholars Program} \faExternalLink \\


\vspace{1mm}

\header{\textbf{Technical Skills}}



\textbf{Languages and Frameworks}: Java, HTML5, CSS3, Javascript,Typescript, React, Redux, Bootsrap \\
\textbf{Tools}: MongoDB, AWS, Figma, Git, Github, Windows, MacOS, Excel, Airtable, \LaTeX \\
\textbf{Relevant Coursework}: Intro to Programming with Java, Calculus 1 \\
\vspace{1mm}

%%==== Experience ====%

\header{\textbf{Technical Experience}}
\href{https://www.memoryglass.net}{\textbf{Memory Glass}}  \faExternalLink, \href{https://epics.engineering.asu.edu/}{\textit{Engineering Projects in Community Service}} \faExternalLink
\hfill August 2021 - Present\\
\vspace{-3mm}
\begin{itemize}
    \item Coordinated with team to build a prototype webapp with React, Typescript, and Bootstrap in less than 2 weeks, just in time for a pitch competition. 
    \item Integrating AWS with the webapp for users to be able to sign in and intereact with the external hardware, that helps Alzheimer's patients recognize people around them by using facial recognition to project the name and relationship onto their glasses. 
    
\end{itemize}

\textbf{Maze Traversing Autonomous Car}, \textit{FSE100 Class, ASU}
\hfill September 2021 - December 2021\\
\vspace{-3mm}
\begin{itemize}
    \item Successfully built and deployed a self-driving car that can navigate through any given maze, and respond to color cues. 
    \item Devised the algorithm, and used MatLab to program the car while working with a team to meet strict weekly deadlines. 
\end{itemize}

\vspace{-1mm}
    \header{\textbf{Work Experience}}

\textbf{Sports Program Official, } \textit{{\href{https://fitness.asu.edu/programs/intramurals}{Sun Devil Fitness Centre}} \faExternalLink},   \hfill August 2021 - Present\\
\vspace{-3mm}
\begin{itemize}
    \item Serve as an official for 100+ intramural contests and facilitate activities and supervise the set-up and take-down of sports sites and equipment.
    \item Learn both the rules of the game and the mechanics necessary to enforce the rules, and exercise authority in an impartial, firm and controlled manner. 
    \item Identify and reported emergency situations quickly, and follow emergency care procedures in the event of an injury or emergency through implementation of CPR and First-Aid. 
\end{itemize}

\textbf{Undergraduate Research Volunteer, } \textit{\href{https://news.asu.edu/20200225-solutions-data-driven-quest-resilient-power-systems}{ASU Sonoran Visualization Lab} \faExternalLink}, \hfill September 2021 - Present\\
\vspace{-3mm}
\begin{itemize}
    \item Assisting graduate research students with their projects by conducting user studies and analyzing collected data to evaluate visualization systems and techniques \textit{(Still in training)}
\end{itemize}

\textbf{CEO and CHRO, }\textit{{\href{https://myeduvisa.org/}{EduVisa}} \faExternalLink},   \hfill March 2020 - August 2021\\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
	\item Developed effective strategies to grow the organization and led the executive team and an online community of over 2500 members.
	\item Orchestrated multiple online webinars (with software like OBS) and community events, including setting up registrations using Google Forms and Zapier, moderating events and collecting post-event feedback.
	\item Devised an automated workflow to effectively assign over 500 students to their tutors and maintained a database using Airtable, MailChimp, Zapier and Excel.
	\item Recruited over 100 tutors from around the world, enabling our organization to reach out to more students.
\end{itemize}

\textbf{Social Media Marketing Intern, }\textit{{\href{https://www.unschool.in/}{UnSchool}} \faExternalLink},  \hfill August 2020 - August 2020\\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
	\item Identified potential leads and communicated the organisation\textquotesingle{}s Unique Selling Points (USP) to the over 25 customers.
	\item Researched consumer opinions and marketing strategies and made adjustments to current strategies accordingly.
\end{itemize}

\textbf{Workshop Host and Outreach Member, }\textit{hACCESS}  \hfill June 2020 - July 2020\\
\vspace{-3mm}
\begin{itemize} \itemsep 1pt
	\item Hosted Python Workshops over Zoom for over 50 people and answered questions.
	\item Reached out to 10+ companies and organizations via Email for potential sponsorship opportunities and received positive responses
\end{itemize}

\vspace{-2mm}


\header{\textbf{Extracurriculars}}


\textbf{Student Clubs:} CodeDevils, Software Developers Association, Sun Devil Data Science, AI Club \\
\textbf{Hackathons:} Sunhacks, Devils Invent



\vspace{-50mm}
    



\end{document}
