\documentclass[10pt, a4paper]{article}
    \usepackage{fullpage}
    \usepackage[margin=0.5in]{geometry}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[inline]{enumitem}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{hyperref}
    
    \pagestyle{empty}
    \raggedright
    \input{glyphtounicode}

\pdfgentounicode=1

\usepackage{fontawesome}


\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-15pt}\vspace*{3pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}


    \begin{document}




%==== Profile ====%
{\begin{center}
    
	{\Huge \scshape {Omkaar Shenoy}}\\  
	\vspace{2mm}
	(341)-345-7209 $\cdot$ omkaarshenoyos@gmail.com $\cdot$ github.com/omkaarshenoy  $\cdot$ omkaarshenoy.github.io
	
\end{center}


%==== Education ====%

    \header{\textbf{Education}}

    \textbf{B.S. in Computer Science}  \hfill GPA 4.00 | May 2025 (expected)
    \\ Arizona State University \hfill Tempe, Arizona
\\Minor in Statistics \\
\textbf{Relevant Coursework}: Object-Oriented Programming and Data Structures, Digital Design, Calculus 1/2 \\


\vspace{2mm}



%%==== Experience ====%

    \header{\textbf{Work Experience}}
    \textbf{Software Developer Intern}, \textit{National Public Radio}     \hfill June 2022 - August 2022\\
    \vspace{-2mm}
\begin{itemize}
    \itemsep-0.05em
    \item Researched and implemented iOS Smart Banners on all npr.org pages using PHP, and deployed the feature to over 50 million monthly NPR users leading to a 10\% increase in NPR One App usage. 
    \item Collaborated with designers and followed Agile development processes to develop and deploy the product page for the NPR One app using HTML, SCSS and Javascript. 
    \item SSHed into servers to upload new image assets, perform e-commerce republishing and run data migration scripts. 
    \item Learned processes of development like collaborating with Git, using DevOps systems and building to different environments for QA testing.
\end{itemize}

    \textbf{Teaching Assistant}, \textit{FSE} 404 \textit{- Engineering Projects in Community Service} \hfill January 2022 - Present\\
      
    \begin{itemize}
        \vspace{-2mm}
        \itemsep-0.05em
        \item Assisted over 50 students every week to make progress on their project, prepare for pitch competitions, and meet deadlines with results. 
        \item Guided students on programming concepts for their projects, good implementation of code, and preparing design documents.
        \item Hosted two hour long skill sessions for 100+ students on how to develop technical skills like Java and how to use Tableau.
    \end{itemize}


\header{\textbf{Projects}}
\textbf{Tiny Desk 3D Visualization}
\hfill July 2022\\
\vspace{-2mm}
\begin{itemize}
    \itemsep-0.05em
    \item Created a three-dimensional visualization of the history of NPR Tiny desk using Three.js for NPR's internal hackathon event and presented it to the Digital Media department. 
    \item Collaboated virtually with a team to collect, clean and analyze data from the last 13 years of Tiny Desk concerts.
\end{itemize}
\textbf{Diabetes Predictor}
\hfill February 2022\\
\vspace{-2mm}
\begin{itemize}
    \itemsep-0.05em
    \item Applied the RandomForestClassifier algorithm, and used Python and pandas to train a Machine learning model to predict the possibility of onset of diabetes based on factors like Age, Insulin levels, and genetics.
    \item Used Streamlit to build, display statistics and visualizations and host this model online. 
\end{itemize}
\textbf{Memory Glass}
\hfill August 2021 - May 2022\\
\vspace{-2mm}
\begin{itemize}
    \itemsep-0.05em
    \item Designed webapp in Figma and coordinated with team to build a functional prototype webapp with React, Typescript, and Node.js in less than 2 weeks, in time for a pitch competition. 
    \item Integrated MySQL with the webapp for users to be able to sign in and interact with external hardware.
    
\end{itemize}

\textbf{Maze Traversing Autonomous Car}
\hfill September 2021 - December 2021\\
\vspace{-2mm}
\begin{itemize}
    \itemsep-0.05em
    \item Designed and deployed a self-driving car that can navigate through any given configuration of a maze in under 2 minutes, and respond to color cues to start, pause and stop the car, as well as pick up and drop off passengers. 
    \item Devised the algorithm, and leveraged MATLab to program the car, and set up external sensors while working with a team to meet strict weekly deadlines. 
\end{itemize}

\header{\textbf{Leadership}}
\textbf{Intramural Manager, } \textit{Sun Devil Fitness Centre}   \hfill August 2021 - Present\\
\vspace{-2mm}
\begin{itemize}
    \itemsep-0.05em
    \item Managed upto 15 intramural matches and 10+ referees per night, and ensured emergency situations were assisted quickly while following emergency care procedures and implementation of CPR and First-Aid, if needed.  
    \item Devised a system to record and verify referee whistle points using Airtable and Zapier. Responded to emails and phone calls and provided customer care to patrons.
\end{itemize}

\header{\textbf{Technical Skills}}

\textbf{Languages and Frameworks}: Java, Python, HTML, SCSS, Sass, Javascript, Typescript, React, Redux, MySQL \\
\textbf{Tools}: AWS, Figma, Git, Github, Windows, MacOS, Excel, Airtable, \LaTeX, Tableau \\
\vspace{3mm}

\header{\textbf{Extracurriculars}}


\textbf{Student Clubs:} CodeDevils, Software Developers Association, Sun Devil Data Science, AI Club \\
\textbf{Hackathons:} Sunhacks, Devils Invent




    



\end{document}
